\documentclass[12pt]{article}
\usepackage[table]{xcolor}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage[english]{babel}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{blkarray}
\usepackage{float}
\usepackage{bm}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{siunitx}

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{proposition}
\newtheorem{exmp}{Example}[section]\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}
\newtheorem{ex}{Exercise}
\theoremstyle{definition}
\theoremstyle{remark}
\bibliographystyle{elsarticle-num}

\DeclareMathOperator{\sinc}{sinc}
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\matindex}[1]{\mbox{\scriptsize#1}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\prob}{\mathbb{P}}

\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}

\begin{document}
\title{Summary next steps}
\author{Renzo Miguel Caballero Rosas} 
\maketitle

\section{Steps:}

\begin{enumerate}

\item Solve the bi-level relaxed problem. Plot $\tilde{\phi}^{(4)}_T(t,v^{(1)},v^{(4)})$ (virtual control) and $\hat{\phi}^{(1)}_T(t-Z_{4,1},v^{(1)},v^{(4)})$ (optimal turbined flow from Bonete at time $t-Z_{4,1}$). Also compute
\begin{equation*}
\int_{Z_{4,1}}^T\int_{\underline{V}^{(1)}}^{\overline{V}^{(1)}}\int_{\underline{V}^{(4)}}^{\overline{V}^{(4)}}\left(\tilde{\phi}^{(4)}_T(t,v^{(1)},v^{(4)})-\hat{\phi}^{(1)}_T(t-Z_{4,1},v^{(1)},v^{(4)})\right)^2dtdv^{(1)}dv^{(4)}.
\end{equation*}

\item Find a primal feasible solution using \textbf{Augmented Lagrangian method}. Here we consider our optimal Lagrange multilayer $\lambda^*(t)$ and we add a penalization function to the cost
\begin{equation*}
\mathcal{L}(\Phi,\bm{V},\lambda^*)+\rho||g(\Phi)(t)||^2_{L^2([0,T]\subset\R)}
\end{equation*}
with
\begin{equation*}
g(\Phi(t))=\begin{cases}
0\ &\text{if}\ t\in[0,Z_{4,1})\\
\left(\tilde{\phi}^{(4)}_T(t)-\hat{\phi}^{(1)}_T(t-Z_{4,1})\right)\ &\text{if}\ t\in[Z_{4,1},T].
\end{cases}
\end{equation*}
Then (we simplify the notation of the norm $||\cdot||_{L^2([0,T]\subset\R)}\to||\cdot||_2$)
\begin{equation*}
\rho||g(\Phi)(t)||^2_2=\begin{cases}
0\ &\text{if}\ t\in[0,Z_{4,1})\\
\rho\left(||\tilde{\phi}^{(4)}_T||^2_2+||\hat{\phi}^{(1)}_T||^2_2-2\left(\tilde{\phi}^{(4)}_T,\hat{\phi}^{(1)}_T\right)_2\right)\ &\text{if}\ t\in[Z_{4,1},T].
\end{cases}
\end{equation*}
Then we do a Taylor expansion for the last therm over the solution in the iteration $K$
\begin{equation*}
\left(\tilde{\phi}^{(4)}_T,\hat{\phi}^{(1)}_T\right)_2\approx\left(\tilde{\phi}^{(4)}_{T_K},\hat{\phi}^{(1)}_{T_K}\right)_2+\left(\tilde{\phi}^{(4)}_{T_K},\hat{\phi}^{(1)}_T-\hat{\phi}^{(1)}_{T_K}\right)_2+\left(\tilde{\phi}^{(4)}_T-\tilde{\phi}^{(4)}_{T_K},\hat{\phi}^{(1)}_{T_K}\right)_2.
\end{equation*}

\item Compute the duality gap.

\item Couple all the dams without wind.

\item Add all the dams.

\item Coupled dam system with wind,

\item Add battery and flexible demand.

\end{enumerate}

\section{Questions and remarks:}

\begin{enumerate}
\item[Q:] What about monotonicity? How does it change when we add the relaxation?

\item[Q:] What about duality gap with concatenated and NO concatenated systems?

\item[Q:] Which is the intuitive value of $\lambda(t)$?

\item[Q:] What about regularity?

\item[R:] I need to parallelize all.
\end{enumerate}

\end{document}