\PassOptionsToPackage{table}{xcolor}
\documentclass[aspectratio=169]{beamer}\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{amsmath,mathtools}
\usepackage{booktabs}
\usepackage{mathptmx}
\usepackage[11pt]{moresize}
\usepackage{hyperref}
\usepackage{bbm}
\usepackage{subfigure}

\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=5mm,text margin right=5mm}
\setbeamertemplate{caption}[numbered]
\addtobeamertemplate{navigation symbols}{}{
\usebeamerfont{footline}
\usebeamercolor[fg]{footline}
\hspace{1em}
\insertframenumber/\inserttotalframenumber}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\I}{\mathbb{I}}

\title{Particular Problems}
\subtitle{Renzo Miguel Caballero Rosas}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\setbeamercolor{background canvas}{bg=blue!10}
\begin{frame}\frametitle{Problem 1: Model}
Deterministic setting, testing nonlinearities in the Dam models.
\begin{enumerate}
\item Generators: Salto Grande, Bonete, and one thermal unit.
\item Demand: deterministic, no flexible demand.
\end{enumerate}
\end{frame}

\setbeamercolor{background canvas}{bg=blue!10}
\begin{frame}\frametitle{Problem 1: Salto Grande}
Salto Grande is a dam, it is totally determined by its state system
\begin{equation*}
\begin{cases}
dV_4(t)=(I_{T_4}(t)-\phi_{R_4}(t))dt+\sigma_{H_4}dW_{H_4}(t)\\
V_4(t_0)=5000\ hm^3\\
t\in[t_0,T]=[0,24]\ hs\\
\phi_{R_4}(t)=\phi_{T_4}(t)+\phi_{P_4}(t)\\
0\leq\phi_{T_4}(t)\leq4200\mathbbm{1}_{\{V_i(t)>\underline{V}_i\}}\ m^3/s\\
0\leq\phi_{P_4}(t)\leq56000\mathbbm{1}_{\{V_i(t)>\underline{V}_i\}}\ m^3/s\\
\end{cases}
\end{equation*}
Its power and cost function are
\begin{equation*}
P_{H_4}=8.72\phi_{H_4}(H_4-5.5),\ C_{H_4}(24)=-
\end{equation*}




\end{frame}

















\setbeamercolor{background canvas}{bg=red!10}
\begin{frame}\frametitle{Problem 2: Model}
Deterministic setting, testing Lagrangian relaxation to deal with coupled Dams.
\begin{enumerate}
\item Generators: Salto Grande, Bonete, Baygorria, Palmar and one thermal unit.
\item Demand: deterministic, no flexible demand.
\end{enumerate}
\end{frame}

\setbeamercolor{background canvas}{bg=green!10}
\begin{frame}\frametitle{Problem 3: Model}
Stochastic setting, testing the effect of wind power in the system.
\begin{enumerate}
\item Generators: Salto Grande, Bonete, Wind Power generators and one thermal unit.
\item Demand: deterministic, no flexible demand.
\end{enumerate}
\end{frame}

\setbeamercolor{background canvas}{bg=yellow!10}
\begin{frame}\frametitle{Problem 4: Model}
Stochastic Setting, testing the effect of wind power in the system and the flexible demand.
\begin{enumerate}
\item Generators: Salto Grande, Bonete, Wind Power generators and one thermal unit.
\item Demand: deterministic, with flexible demand.
\end{enumerate} 
\end{frame}

\end{document}