% Acknowledgments File

\begin{center}
•
\end{center}
\begin{center}

{\bf\fontsize{14pt}{14.5pt}\selectfont \uppercase{Acknowledgements}}\\\vspace{1cm}
\end{center}

\addcontentsline{toc}{chapter}{Acknowledgements}

\textit{I would like to thank all the people who contribute in my work, especially to:}
\begin{enumerate}

\item \textit{Prof. Ra\'ul Tempone for being my supervisor and for accepting me as a member of his research group for the last two years. I am really grateful for his assistance and guidance throughout my Master degree.}

\item \textit{Prof. Claudio Risso for all the invaluable cooperation along with my work. }

\item \textit{Prof. Marco Scavino for all his disposition to help and for being the professor who introduced KAUST to me.}

\item \textit{Prof. Jesper Oppelstrup for his extremely useful advises during the critical moments of this work.}

\item \textit{Dr. S\"{o}ren Wolfers for all his time spent in my work and teaching me the needed concepts and tools.}

\end{enumerate}
\textit{Also, I would like to thank my friends, family, and fianc\'e for all their support and tolerance during the time of this work.\\
Finally, I would like to thank KAUST an all its community for making the realization of this work possible.}\\
!`MUCHAS GRACIAS! %Please remove this code taking particular care to remove the \textit command which makes use of italic font.

% Copyright 2010 Imran Shafique Ansari
% Contact Email: imran.ansari@kaust.edu.sa
% Contact Number: +966 59 897 1005

% Modified by Said Ehrlich